Competing Bandits

### 2018-08-09 analysis_code/eeog.Rmd
update analysis code + pdf results

WORKING_PATH <- "/Users/garidor/Desktop/bandits-rl-project/results/tournament_raw_results/"
f <- "tournament_experiment_ws_small_erase_rep_raw.csv"
dat <- read.csv(file=paste(WORKING_PATH, f, sep=""))
#dat_2 <- read.csv(file=paste(WORKING_PATH, "tournament_experiment_tourn_.5_.7_raw.csv", sep=""))
#dat <- rbind(dat, dat_2)
dat <- filter(dat, Time.Horizon == 5000)
priors <- as.list(unique(dat['Prior']))$Prior
warm_starts <- as.list(unique(dat['Warm.Start']))$Warm.Start
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")

for (prior in priors) {
  results <- matrix(nrow=3, ncol=length(warm_starts))
  rownames(results) <- c("TS vs DG", "TS vs DEG", "DG vs DEG")
  colnames(results) <- lapply(warm_starts, function (start) { return(paste("WS =", start))})
  for (i in 1:length(warm_starts)) {
    warm_start = warm_starts[i]
    for (k in 1:length(algs)) {
      for (l in 1:length(algs)) {
        p1alg = algs[k]
        p2alg = algs[l]
        filtered_dat <- filter(dat, Prior == prior & Agent.Alg == "HardMax" & Warm.Start == warm_start & P1.Alg == p1alg & P2.Alg == p2alg)
        if (nrow(filtered_dat) == 0) { next }
        share <- filtered_dat$Market.Share.for.P1
        test <- t.test(share)
        cin <- signif(test$conf.int[2] - mean(share), digits=1)
        eeog_mean <- signif(mean(filtered_dat$EEOG), digits=2)
        eeog_summary <- summary(filtered_dat$EEOG)
        res_text <- paste("<b>",signif(mean(share), digits=2), "</b> (", cin, ")<br><u>eeog</u><br> avg: ", eeog_mean, "<br>med: ", eeog_summary["Median"] , sep="")
        if (p1alg == "ThompsonSampling" && p2alg == "DynamicGreedy") {
          results[1, i] <- res_text
        } else if (p1alg == "ThompsonSampling" && p2alg == "DynamicEpsilonGreedy") {
          results[2, i] <- res_text
        } else if (p1alg == "DynamicGreedy" && p2alg == "DynamicEpsilonGreedy") {
          results[3, i] <- res_text
        }
      }
    }
  }
  tab <-xtable(results, caption=paste("Results for", prior, "HardMax", "K=10, erased reputation"))
  print(tab, type="html")
  if (prior != ".5/.7 Random Draw") {   print("<br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br>") }

>>>>

WORKING_PATH <- "/Users/garidor/Desktop/bandits-rl-project/results/tournament_raw_results/"
f <- "tournament_experiment_test_raw.csv"
dat <- read.csv(file=paste(WORKING_PATH, f, sep=""))
#dat_2 <- read.csv(file=paste(WORKING_PATH, "tournament_experiment_tourn_.5_.7_raw.csv", sep=""))
#dat <- rbind(dat, dat_2)
dat <- filter(dat, Time.Horizon == 2000)
#priors <- as.list(unique(dat['Prior']))$Prior
priors <- c("Heavy Tail")
#warm_starts <- as.list(unique(dat['Warm.Start']))$Warm.Start
warm_starts <- c(20, 50, 100)
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")

for (prior in priors) {
  results <- matrix(nrow=3, ncol=length(warm_starts))
  rownames(results) <- c("TS vs DG", "TS vs DEG", "DG vs DEG")
  colnames(results) <- lapply(warm_starts, function (start) { return(paste("k =", start))})
  for (i in 1:length(warm_starts)) {
    warm_start = warm_starts[i]
    for (k in 1:length(algs)) {
      for (l in 1:length(algs)) {
        p1alg = algs[k]
        p2alg = algs[l]
        filtered_dat <- filter(dat, Prior == prior & Agent.Alg == "HardMax" & Warm.Start == warm_start & P1.Alg == p1alg & P2.Alg == p2alg)
        if (nrow(filtered_dat) == 0) { next }
        share <- filtered_dat$Market.Share.for.P1
        test <- t.test(share)
        cin <- signif(test$conf.int[2] - mean(share), digits=1)
        eeog_mean <- signif(mean(filtered_dat$EEOG), digits=2)
        eeog_summary <- summary(filtered_dat$EEOG)
        res_text <- paste("<b>",signif(mean(share), digits=2), "</b> (", cin, ")<br><u>eeog</u><br> avg: ", eeog_mean, "<br>med: ", eeog_summary["Median"] , sep="")
        if (p1alg == "ThompsonSampling" && p2alg == "DynamicGreedy") {
          results[1, i] <- res_text
        } else if (p1alg == "ThompsonSampling" && p2alg == "DynamicEpsilonGreedy") {
          results[2, i] <- res_text
        } else if (p1alg == "DynamicGreedy" && p2alg == "DynamicEpsilonGreedy") {
          results[3, i] <- res_text
        }
      }
    }
  }
  tab <-xtable(results, caption=paste("Results for", prior, "HardMax", "K=10"))
  print(tab, type="html")

### 2018-08-09 analysis_code/tournament_table.Rmd
update analysis code + pdf results

#dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_parallel_test_raw.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_free_obs_10_arms_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(5000)
priors <- as.list(unique(dat['Prior']))$Prior

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
alg_names <- c("Thompson Sampling", "Dynamic Epsilon Greedy", " DynamicGreedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (j in 1:length(time_horizons)) {
  for (prior in priors) {
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      print_breaks <- FALSE
        time <- time_horizons[j]
        results <- matrix(nrow=length(algs), ncol=length(algs))
        colnames(results) <- alg_names
        rownames(results) <- alg_names
        for (k in 1:length(algs)) {
          for (l in 1:length(algs)) {
            p1alg = algs[k]
            p2alg = algs[l]
            filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Warm.Start == 5 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
            if (nrow(filtered_dat) == 0) {
              if (p1alg == p2alg) { print_breaks <- TRUE }
              next
            }
            share <- filtered_dat$Market.Share.for.P1
            test <- t.test(share)
            cin <- signif(test$conf.int[2] - mean(share), digits=2)
            shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
            cv_high <- qchisq(.975, df=length(share) - 1)
            cv_low <- qchisq(.025, df=length(share) - 1)
            lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=2)
            high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=2)
            results[k, l] <- paste("<b>", signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", 100*signif(shares, digits=2), "%")
          }
        }
        tab <-xtable(results, caption=paste("Results for", agent_alg, "t =", time, prior, "200 free obs", "K =", 10))
        print(tab, type="html")
        if (print_breaks) { print("<br>") }
      }
    }
  }

>>>>

dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_testing_prelim_raw.csv", sep=""))
#dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_free_obs_10_arms_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(2000)
priors <- as.list(unique(dat['Prior']))$Prior

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
alg_names <- c("Thompson Sampling", "Dynamic Epsilon Greedy", " DynamicGreedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (j in 1:length(time_horizons)) {
  for (prior in priors) {
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      print_breaks <- FALSE
        time <- time_horizons[j]
        results <- matrix(nrow=length(algs), ncol=length(algs))
        colnames(results) <- alg_names
        rownames(results) <- alg_names
        for (k in 1:length(algs)) {
          for (l in 1:length(algs)) {
            p1alg = algs[k]
            p2alg = algs[l]
            filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Warm.Start == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
            if (nrow(filtered_dat) == 0) {
              if (p1alg == p2alg) { print_breaks <- TRUE }
              next
            }
            share <- filtered_dat$Market.Share.for.P1
            test <- t.test(share)
            cin <- signif(test$conf.int[2] - mean(share), digits=2)
            shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
            cv_high <- qchisq(.975, df=length(share) - 1)
            cv_low <- qchisq(.025, df=length(share) - 1)
            lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=2)
            high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=2)
            results[k, l] <- paste("<b>", signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", 100*signif(shares, digits=2), "%")
          }
        }
        tab <-xtable(results, caption=paste("Results for", agent_alg, "t =", time, prior, "200 free obs", "K =", 10))
        print(tab, type="html")
        if (print_breaks) { print("<br>") }
      }
    }
  }

### 2018-08-09 paper/competing_bandits.tex
update analysis code + pdf results

 \author{-}
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\

@@

\begin{table}[ht]
\centering
\caption{Simultaneous Entry Needle In Haystack} 
\begin{tabular}{rlll}
  \hline
 & k = 20 & k = 100 & k = 200 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.86} $\pm$0.02\\ eeog \\ avg: 14\\ med: 0} & \makecell{\textbf{0.65} $\pm$0.02\\ eeog \\ avg: 11\\ med: 0} & \makecell{\textbf{0.59} $\pm$0.02\\ eeog \\ avg: 6\\ med: 0} \\ 
  TS vs DEG & \makecell{\textbf{0.84} $\pm$0.02\\ eeog \\ avg: 20\\ med: 0} & \makecell{\textbf{0.62} $\pm$0.02\\ eeog \\ avg: 8\\ med: 0} & \makecell{\textbf{0.51} $\pm$0.03\\ eeog \\ avg: 5.4\\ med: 0} \\ 
  DG vs DEG & \makecell{\textbf{0.41} $\pm$0.02\\ eeog \\ avg: 400\\ med: 115} & \makecell{\textbf{0.47} $\pm$0.02\\ eeog \\ avg: 320\\ med: 0} & \makecell{\textbf{0.5} $\pm$0.02\\ eeog \\ avg: 290\\ med: 0} \\ 
   \hline
   \label{hm_nih}
\end{tabular}
\caption*{\tiny{The first line in each cell contains the average market share received by the firm playing Alg 1 (and the market share of Alg 2 is 1 - Alg 1 Market Share) as well as a 95 \% confidence band. For example, the cell in the top left indicates that TS gets on average 32\% of the market when played against DG. The next line contain the average and median effective end of game for this set of simulations.}}
\end{table}

\begin{table}[ht]
\centering
\caption{Simultaneous Entry Heavy Tail} 
\begin{tabular}{rlll}
  \hline
 & k = 20 & k = 100 & k = 200 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.22} $\pm$0.02\\ eeog \\ avg: 0.27\\ med: 0} & \makecell{\textbf{0.41} $\pm$0.02\\ eeog \\ avg: 0.039\\ med: 0} & \makecell{\textbf{0.58} $\pm$0.02\\ eeog \\ avg: 12\\ med: 0} \\ 
  TS vs DEG & \makecell{\textbf{0.24} $\pm$0.02\\ eeog \\ avg: 3.2\\ med: 0} & \makecell{\textbf{0.48} $\pm$0.02\\ eeog \\ avg: 39\\ med: 0} & \makecell{\textbf{0.91} $\pm$0.01\\ eeog \\ avg: 84\\ med: 0} \\ 
  DG vs DEG & \makecell{\textbf{0.8} $\pm$0.02\\ eeog \\ avg: 16\\ med: 0} & \makecell{\textbf{0.86} $\pm$0.02\\ eeog \\ avg: 4.7\\ med: 0} & \makecell{\textbf{0.83} $\pm$0.02\\ eeog \\ avg: 2.7\\ med: 0} \\ 
   \hline
   \label{hm_ht}
\end{tabular}
\end{table}

>>>>

\author{Guy Aridor \\
g.aridor@columbia.edu \\
Columbia University \\ Department of Economics\\
	\And Kevin Liu\\
	kevin.liu@columbia.edu \\
	Columbia University \\Department of Computer Science\\
	\AND Alex Slivkins \\
	slivkins@microsoft.edu\\
	Microsoft Research NYC\\
	 \\ 
	\And Steven Wu\\
	zsw@umn.edu\\	
	University of Minnesota - Twin Cities \\Department of Computer Science\\	
}
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\

@@

\begin{table}[ht]
\centering
\caption{Simultaneous Entry Needle In Haystack} 
\begin{tabular}{rlll}
  \hline
 & k = 20 & k = 100 & k = 200 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.66} $\pm$0.02\\ eeog \\ avg: 190\\ med: 26} & \makecell{\textbf{0.62} $\pm$0.02\\ eeog \\ avg: 240\\ med: 32} &  \\ 
  TS vs DEG & \makecell{\textbf{0.61} $\pm$0.02\\ eeog \\ avg: 150\\ med: 12} & \makecell{\textbf{0.55} $\pm$0.02\\ eeog \\ avg: 240\\ med: 26} &  \\ 
  DG vs DEG & \makecell{\textbf{0.44} $\pm$0.02\\ eeog \\ avg: 360\\ med: 106} & \makecell{\textbf{0.44} $\pm$0.02\\ eeog \\ avg: 590\\ med: 312} &  \\ 
   \hline
   \label{hm_nih}
\end{tabular}
\caption*{\tiny{The first line in each cell contains the average market share received by the firm playing Alg 1 (and the market share of Alg 2 is 1 - Alg 1 Market Share) as well as a 95 \% confidence band. For example, the cell in the top left indicates that TS gets on average 32\% of the market when played against DG. The next line contain the average and median effective end of game for this set of simulations.}}
\end{table}

\begin{table}[ht]
\centering
\caption{Simultaneous Entry Heavy Tail} 
\begin{tabular}{rlll}
  \hline
 & k = 20 & k = 100 & k = 200 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.33} $\pm$0.02\\ eeog \\ avg: 49\\ med: 0} & \makecell{\textbf{0.52} $\pm$0.02\\ eeog \\ avg: 120\\ med: 0} &  \\ 
  TS vs DEG & \makecell{\textbf{0.3} $\pm$0.02\\ eeog \\ avg: 26\\ med: 0} & \makecell{\textbf{0.58} $\pm$0.02\\ eeog \\ avg: 160\\ med: 0} &  \\ 
  DG vs DEG & \makecell{\textbf{0.62} $\pm$0.02\\ eeog \\ avg: 350\\ med: 4} & \makecell{\textbf{0.6} $\pm$0.02\\ eeog \\ avg: 650\\ med: 398.5} &  \\ 
   \hline
   \label{hm_ht}
\end{tabular}
\end{table}
